---
title: "sp"
format: revealjs
editor: visual
---

# Relationship between species abundance and predictors

## Menu

```{r}
bdd_sp_explo=bdd_sp

id_col=c("ID","Programme","Annee","ID_Site","Protocole")
vdt_col=c("AB_tot", "BM_tot", "Richesse_tot")
land_cover_col=c("clcm_lvl3")
topo_col=c("elevation","gps_x","gps_y")
soil_col=c("ph_0_a_30","sable.0_30","limon.0_30","argile.0_30","c_orga_0_a_30","P","N","K","CN","CEC","CaCO3")

climate_col=c()
for (i in 1:19){
  climate_col=c(climate_col, paste0("bio",i) )
}
climate_col=c(climate_col,"cmi_mean","gdd0","gdd10","hurs_mean","pet_penman_mean")

bdd_sp_explo= bdd_sp[,c(id_col,vdt_col,land_cover_col,topo_col,soil_col,climate_col,col_ab)]
bdd_sp_explo$ID = as.factor(bdd_sp_explo$ID)


# Renome
new_soil_col=c("pH","sand","silt","clay","C","P","N","K","CN","CEC","CaCO3")
new_soil_col=c("pH","sand","silt","clay","C","P","N","K","CN","CEC","CaCO3")
bdd_sp_explo <- rename(bdd_sp_explo, !!setNames(soil_col, new_soil_col))

bdd_sp_explo <- bdd_sp_explo %>% 
  rename(PET = pet_penman_mean)
climate_col=c()
for (i in 1:19){
  climate_col=c(climate_col, paste0("bio",i) )
}
climate_col=c(climate_col,"cmi_mean","gdd0","gdd10","hurs_mean","PET")


col_graph=c(vdt_col,land_cover_col,topo_col,new_soil_col,climate_col)



predictors = c("gps_x" ,"gps_y" ,"CN" ,"K" ,"CaCO3" ,"N" ,"clay" ,"P" ,"bio4" ,"CEC" ,"silt" ,"PET" ,"bio13" ,"sand" ,"bio19" ,"cmi_mean" ,"bio15" ,"gdd10" ,"hurs_mean")


# for (j in col_ab) {
#   cat(paste0("[",j,"]\n\n"))
# }
```

[AB_Allolobophora_chlorotica_chlorotica]

[AB_Aporrectodea_caliginosa]

[AB_Aporrectodea_rosea]

[AB_Lumbricus_terrestris]

[AB_Lumbricus_castaneus]

[AB_Aporrectodea_longa_longa]

[AB_Aporrectodea_icterica]

[AB_Aporrectodea_giardi]

[AB_Lumbricus_sp]

[AB_Aporrectodea_nocturna]

[AB_Satchellius_mammalis]

[AB_Aporrectodea_sp]

[AB_Aporrectodea_caliginosa_meridionalis]

[AB_Octolasion_cyaneum]

[AB_Lumbricus_rubellus_rubellus]

[AB_Lumbricus_friendi]

[AB_Murchieona_muldali]

[AB_Lumbricus_rubellus_castanoides]

[AB_Lumbricus_centralis]

[AB_Octolasion_sp]

[AB_Allolobophora_chlorotica_postepheba]

[AB_Lumbricus_festivus]

[AB_Aporrectodea_ind√©terminable](#ab_aporrectodea_ind„terminable)

[AB_Proctodrilus_antipai_antipai]

[AB_Aporrectodea_caliginosa_ind√©terminable](#ab_aporrectodea_caliginosa_ind„terminable)

[AB_Allolobophora_sp]

[AB_Lumbricus_castaneus_disjonctus]

[AB_Eisenia_fetida]

[AB_Dendrobaena_octaedra]

[AB_Aporrectodea_trapezoides]

[AB_Eiseniella_tetraedra]

[AB_Lumbricus_rubellus_ind√©terminable](#ab_lumbricus_rubellus_ind„terminable)

[AB_Eisenia_andrei]

[AB_Aporrectodea_cupulifera]

[AB_Dendrodrilus_rubidus]

[AB_Dendrobaena_attemsi]

[AB_Prosellodrilus_amplisetosus_amplisetosus]

[AB_Aporrectodea_georgii]

[AB_Dendrobaena_sp]

[AB_Avelona_ligra]

[AB_Octolasion_lacteum_lacteum]

[AB_Allolobophora_burgondiae]

[AB_Aporrectodea_ripicola]

[AB_Prosellodrilus_fragilis_ind√©terminable](#ab_prosellodrilus_fragilis_ind„terminable)

```{r gener code}
# code <- NULL
# for (var_rep in col_ab) {
# code <- generate_species_code(var_rep)
# writeLines(code, paste0("sp/",var_rep, ".qmd") )
# }
# 
# 
# 
# script_contents <- list()
# for (var_rep in col_ab) {
#   script_contents[[var_rep]] <- readLines(paste0("sp/", var_rep, ".qmd"))
# }
# combined_content <- unlist(script_contents)
# writeLines(combined_content, "sp/combined_script.qmd")

```

## AB_Allolobophora_chlorotica_chlorotica

[Menu]

```{r  AB_Allolobophora_chlorotica_chlorotica , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Allolobophora_chlorotica_chlorotica'
titre <- paste('
AB_Allolobophora_chlorotica_chlorotica
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Aporrectodea_caliginosa

[Menu]

```{r  AB_Aporrectodea_caliginosa , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_caliginosa'
titre <- paste('
AB_Aporrectodea_caliginosa
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Aporrectodea_rosea

[Menu]

```{r  AB_Aporrectodea_rosea , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_rosea'
titre <- paste('
AB_Aporrectodea_rosea
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Lumbricus_terrestris

[Menu]

```{r  AB_Lumbricus_terrestris , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_terrestris'
titre <- paste('
AB_Lumbricus_terrestris
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Lumbricus_castaneus

[Menu]

```{r  AB_Lumbricus_castaneus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_castaneus'
titre <- paste('
AB_Lumbricus_castaneus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Aporrectodea_longa_longa

[Menu]

```{r  AB_Aporrectodea_longa_longa , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_longa_longa'
titre <- paste('
AB_Aporrectodea_longa_longa
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Aporrectodea_icterica

[Menu]

```{r  AB_Aporrectodea_icterica , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_icterica'
titre <- paste('
AB_Aporrectodea_icterica
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Aporrectodea_giardi

[Menu]

```{r  AB_Aporrectodea_giardi , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_giardi'
titre <- paste('
AB_Aporrectodea_giardi
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Lumbricus_sp

[Menu]

```{r  AB_Lumbricus_sp , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_sp'
titre <- paste('
AB_Lumbricus_sp
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Aporrectodea_nocturna

[Menu]

```{r  AB_Aporrectodea_nocturna , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_nocturna'
titre <- paste('
AB_Aporrectodea_nocturna
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Satchellius_mammalis

[Menu]

```{r  AB_Satchellius_mammalis , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Satchellius_mammalis'
titre <- paste('
AB_Satchellius_mammalis
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Aporrectodea_sp

[Menu]

```{r  AB_Aporrectodea_sp , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_sp'
titre <- paste('
AB_Aporrectodea_sp
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Aporrectodea_caliginosa_meridionalis

[Menu]

```{r  AB_Aporrectodea_caliginosa_meridionalis , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_caliginosa_meridionalis'
titre <- paste('
AB_Aporrectodea_caliginosa_meridionalis
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Octolasion_cyaneum

[Menu]

```{r  AB_Octolasion_cyaneum , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Octolasion_cyaneum'
titre <- paste('
AB_Octolasion_cyaneum
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Lumbricus_rubellus_rubellus

[Menu]

```{r  AB_Lumbricus_rubellus_rubellus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_rubellus_rubellus'
titre <- paste('
AB_Lumbricus_rubellus_rubellus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Lumbricus_friendi

[Menu]

```{r  AB_Lumbricus_friendi , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_friendi'
titre <- paste('
AB_Lumbricus_friendi
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Murchieona_muldali

[Menu]

```{r  AB_Murchieona_muldali , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Murchieona_muldali'
titre <- paste('
AB_Murchieona_muldali
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Lumbricus_rubellus_castanoides

[Menu]

```{r  AB_Lumbricus_rubellus_castanoides , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_rubellus_castanoides'
titre <- paste('
AB_Lumbricus_rubellus_castanoides
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Lumbricus_centralis

[Menu]

```{r  AB_Lumbricus_centralis , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_centralis'
titre <- paste('
AB_Lumbricus_centralis
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Octolasion_sp

[Menu]

```{r  AB_Octolasion_sp , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Octolasion_sp'
titre <- paste('
AB_Octolasion_sp
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Allolobophora_chlorotica_postepheba

[Menu]

```{r  AB_Allolobophora_chlorotica_postepheba , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Allolobophora_chlorotica_postepheba'
titre <- paste('
AB_Allolobophora_chlorotica_postepheba
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Lumbricus_festivus

[Menu]

```{r  AB_Lumbricus_festivus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_festivus'
titre <- paste('
AB_Lumbricus_festivus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Aporrectodea_ind√©terminable {#ab_aporrectodea_ind„terminable}

[Menu]

```{r  AB_Aporrectodea_ind√©terminable , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_ind√©terminable'
titre <- paste('
AB_Aporrectodea_ind√©terminable
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Proctodrilus_antipai_antipai

[Menu]

```{r  AB_Proctodrilus_antipai_antipai , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Proctodrilus_antipai_antipai'
titre <- paste('
AB_Proctodrilus_antipai_antipai
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Aporrectodea_caliginosa_ind√©terminable {#ab_aporrectodea_caliginosa_ind„terminable}

[Menu]

```{r  AB_Aporrectodea_caliginosa_ind√©terminable , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_caliginosa_ind√©terminable'
titre <- paste('
AB_Aporrectodea_caliginosa_ind√©terminable
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Allolobophora_sp

[Menu]

```{r  AB_Allolobophora_sp , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Allolobophora_sp'
titre <- paste('
AB_Allolobophora_sp
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Lumbricus_castaneus_disjonctus

[Menu]

```{r  AB_Lumbricus_castaneus_disjonctus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_castaneus_disjonctus'
titre <- paste('
AB_Lumbricus_castaneus_disjonctus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Eisenia_fetida

[Menu]

```{r  AB_Eisenia_fetida , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Eisenia_fetida'
titre <- paste('
AB_Eisenia_fetida
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Dendrobaena_octaedra

[Menu]

```{r  AB_Dendrobaena_octaedra , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Dendrobaena_octaedra'
titre <- paste('
AB_Dendrobaena_octaedra
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Aporrectodea_trapezoides

[Menu]

```{r  AB_Aporrectodea_trapezoides , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_trapezoides'
titre <- paste('
AB_Aporrectodea_trapezoides
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Eiseniella_tetraedra

[Menu]

```{r  AB_Eiseniella_tetraedra , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Eiseniella_tetraedra'
titre <- paste('
AB_Eiseniella_tetraedra
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Lumbricus_rubellus_ind√©terminable {#ab_lumbricus_rubellus_ind„terminable}

[Menu]

```{r  AB_Lumbricus_rubellus_ind√©terminable , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_rubellus_ind√©terminable'
titre <- paste('
AB_Lumbricus_rubellus_ind√©terminable
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Eisenia_andrei

[Menu]

```{r  AB_Eisenia_andrei , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Eisenia_andrei'
titre <- paste('
AB_Eisenia_andrei
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Aporrectodea_cupulifera

[Menu]

```{r  AB_Aporrectodea_cupulifera , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_cupulifera'
titre <- paste('
AB_Aporrectodea_cupulifera
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Dendrodrilus_rubidus

[Menu]

```{r  AB_Dendrodrilus_rubidus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Dendrodrilus_rubidus'
titre <- paste('
AB_Dendrodrilus_rubidus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Dendrobaena_attemsi

[Menu]

```{r  AB_Dendrobaena_attemsi , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Dendrobaena_attemsi'
titre <- paste('
AB_Dendrobaena_attemsi
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Prosellodrilus_amplisetosus_amplisetosus

[Menu]

```{r  AB_Prosellodrilus_amplisetosus_amplisetosus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Prosellodrilus_amplisetosus_amplisetosus'
titre <- paste('
AB_Prosellodrilus_amplisetosus_amplisetosus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Aporrectodea_georgii

[Menu]

```{r  AB_Aporrectodea_georgii , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_georgii'
titre <- paste('
AB_Aporrectodea_georgii
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Dendrobaena_sp

[Menu]

```{r  AB_Dendrobaena_sp , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Dendrobaena_sp'
titre <- paste('
AB_Dendrobaena_sp
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Avelona_ligra

[Menu]

```{r  AB_Avelona_ligra , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Avelona_ligra'
titre <- paste('
AB_Avelona_ligra
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Octolasion_lacteum_lacteum

[Menu]

```{r  AB_Octolasion_lacteum_lacteum , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Octolasion_lacteum_lacteum'
titre <- paste('
AB_Octolasion_lacteum_lacteum
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Allolobophora_burgondiae

[Menu]

```{r  AB_Allolobophora_burgondiae , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Allolobophora_burgondiae'
titre <- paste('
AB_Allolobophora_burgondiae
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Aporrectodea_ripicola

[Menu]

```{r  AB_Aporrectodea_ripicola , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_ripicola'
titre <- paste('
AB_Aporrectodea_ripicola
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Prosellodrilus_fragilis_ind√©terminable {#ab_prosellodrilus_fragilis_ind„terminable}

[Menu]

```{r  AB_Prosellodrilus_fragilis_ind√©terminable , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Prosellodrilus_fragilis_ind√©terminable'
titre <- paste('
AB_Prosellodrilus_fragilis_ind√©terminable
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Dendrodrilus_rubidus_subrubicundus

[Menu]

```{r  AB_Dendrodrilus_rubidus_subrubicundus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Dendrodrilus_rubidus_subrubicundus'
titre <- paste('
AB_Dendrodrilus_rubidus_subrubicundus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Scherotheca_sp

[Menu]

```{r  AB_Scherotheca_sp , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Scherotheca_sp'
titre <- paste('
AB_Scherotheca_sp
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Microscolex_dubius

[Menu]

```{r  AB_Microscolex_dubius , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Microscolex_dubius'
titre <- paste('
AB_Microscolex_dubius
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Prosellodrilus_sp

[Menu]

```{r  AB_Prosellodrilus_sp , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Prosellodrilus_sp'
titre <- paste('
AB_Prosellodrilus_sp
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Aporrectodea_tuberculata

[Menu]

```{r  AB_Aporrectodea_tuberculata , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_tuberculata'
titre <- paste('
AB_Aporrectodea_tuberculata
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Scherotheca_savignyi_savignyi

[Menu]

```{r  AB_Scherotheca_savignyi_savignyi , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Scherotheca_savignyi_savignyi'
titre <- paste('
AB_Scherotheca_savignyi_savignyi
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Aporrectodea_longa

[Menu]

```{r  AB_Aporrectodea_longa , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_longa'
titre <- paste('
AB_Aporrectodea_longa
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Eisenia_veneta

[Menu]

```{r  AB_Eisenia_veneta , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Eisenia_veneta'
titre <- paste('
AB_Eisenia_veneta
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Aporrectodea_limicola

[Menu]

```{r  AB_Aporrectodea_limicola , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_limicola'
titre <- paste('
AB_Aporrectodea_limicola
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Microscolex_phosphoreus

[Menu]

```{r  AB_Microscolex_phosphoreus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Microscolex_phosphoreus'
titre <- paste('
AB_Microscolex_phosphoreus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Eisenia_sp

[Menu]

```{r  AB_Eisenia_sp , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Eisenia_sp'
titre <- paste('
AB_Eisenia_sp
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Eisenia_fetida_ind√©terminable

[Menu]

```{r  AB_Eisenia_fetida_ind√©terminable , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Eisenia_fetida_ind√©terminable'
titre <- paste('
AB_Eisenia_fetida_ind√©terminable
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Prosellodrilus_fragilis_fragilis

[Menu]

```{r  AB_Prosellodrilus_fragilis_fragilis , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Prosellodrilus_fragilis_fragilis'
titre <- paste('
AB_Prosellodrilus_fragilis_fragilis
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Lumbricus_friendi_lineatus

[Menu]

```{r  AB_Lumbricus_friendi_lineatus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_friendi_lineatus'
titre <- paste('
AB_Lumbricus_friendi_lineatus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Dendrobaena_cognettii

[Menu]

```{r  AB_Dendrobaena_cognettii , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Dendrobaena_cognettii'
titre <- paste('
AB_Dendrobaena_cognettii
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Dendrobaena_hortensis

[Menu]

```{r  AB_Dendrobaena_hortensis , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Dendrobaena_hortensis'
titre <- paste('
AB_Dendrobaena_hortensis
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Bimastos_eiseni

[Menu]

```{r  AB_Bimastos_eiseni , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Bimastos_eiseni'
titre <- paste('
AB_Bimastos_eiseni
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Allolobophora_chlorotica_ind√©terminable

[Menu]

```{r  AB_Allolobophora_chlorotica_ind√©terminable , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Allolobophora_chlorotica_ind√©terminable'
titre <- paste('
AB_Allolobophora_chlorotica_ind√©terminable
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Lumbricus_rubellus_friendoides

[Menu]

```{r  AB_Lumbricus_rubellus_friendoides , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_rubellus_friendoides'
titre <- paste('
AB_Lumbricus_rubellus_friendoides
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Haplotaxis_sp

[Menu]

```{r  AB_Haplotaxis_sp , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Haplotaxis_sp'
titre <- paste('
AB_Haplotaxis_sp
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Octodrilus_complanatus

[Menu]

```{r  AB_Octodrilus_complanatus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Octodrilus_complanatus'
titre <- paste('
AB_Octodrilus_complanatus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Lumbricus_meliboeus

[Menu]

```{r  AB_Lumbricus_meliboeus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_meliboeus'
titre <- paste('
AB_Lumbricus_meliboeus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Prosellodrilus_occidentalis_occidentalis

[Menu]

```{r  AB_Prosellodrilus_occidentalis_occidentalis , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Prosellodrilus_occidentalis_occidentalis'
titre <- paste('
AB_Prosellodrilus_occidentalis_occidentalis
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Scherotheca_dinoscolex

[Menu]

```{r  AB_Scherotheca_dinoscolex , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Scherotheca_dinoscolex'
titre <- paste('
AB_Scherotheca_dinoscolex
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Dendrobaena_alpina_zeugochaeta

[Menu]

```{r  AB_Dendrobaena_alpina_zeugochaeta , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Dendrobaena_alpina_zeugochaeta'
titre <- paste('
AB_Dendrobaena_alpina_zeugochaeta
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Microscolex_sp

[Menu]

```{r  AB_Microscolex_sp , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Microscolex_sp'
titre <- paste('
AB_Microscolex_sp
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Hemigastrodrilus_monicae

[Menu]

```{r  AB_Hemigastrodrilus_monicae , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Hemigastrodrilus_monicae'
titre <- paste('
AB_Hemigastrodrilus_monicae
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Prosellodrilus_praticola

[Menu]

```{r  AB_Prosellodrilus_praticola , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Prosellodrilus_praticola'
titre <- paste('
AB_Prosellodrilus_praticola
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Octolasion_lacteum

[Menu]

```{r  AB_Octolasion_lacteum , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Octolasion_lacteum'
titre <- paste('
AB_Octolasion_lacteum
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Scherotheca_savignyi_ind√©terminable

[Menu]

```{r  AB_Scherotheca_savignyi_ind√©terminable , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Scherotheca_savignyi_ind√©terminable'
titre <- paste('
AB_Scherotheca_savignyi_ind√©terminable
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Aporrectodea_rubra

[Menu]

```{r  AB_Aporrectodea_rubra , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_rubra'
titre <- paste('
AB_Aporrectodea_rubra
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Scherotheca_rhodana

[Menu]

```{r  AB_Scherotheca_rhodana , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Scherotheca_rhodana'
titre <- paste('
AB_Scherotheca_rhodana
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Pheretima_ind√©terminable

[Menu]

```{r  AB_Pheretima_ind√©terminable , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Pheretima_ind√©terminable'
titre <- paste('
AB_Pheretima_ind√©terminable
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Prosellodrilus_pyrenaicus

[Menu]

```{r  AB_Prosellodrilus_pyrenaicus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Prosellodrilus_pyrenaicus'
titre <- paste('
AB_Prosellodrilus_pyrenaicus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Scherotheca_nivicola

[Menu]

```{r  AB_Scherotheca_nivicola , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Scherotheca_nivicola'
titre <- paste('
AB_Scherotheca_nivicola
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Panoniona_leoni

[Menu]

```{r  AB_Panoniona_leoni , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Panoniona_leoni'
titre <- paste('
AB_Panoniona_leoni
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Pheritima_Diffringens

[Menu]

```{r  AB_Pheritima_Diffringens , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Pheritima_Diffringens'
titre <- paste('
AB_Pheritima_Diffringens
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Scherotheca_aquitana

[Menu]

```{r  AB_Scherotheca_aquitana , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Scherotheca_aquitana'
titre <- paste('
AB_Scherotheca_aquitana
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Proctodrilus_antipai_ind√©terminable

[Menu]

```{r  AB_Proctodrilus_antipai_ind√©terminable , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Proctodrilus_antipai_ind√©terminable'
titre <- paste('
AB_Proctodrilus_antipai_ind√©terminable
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Prosellodrilus_amplisetosus

[Menu]

```{r  AB_Prosellodrilus_amplisetosus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Prosellodrilus_amplisetosus'
titre <- paste('
AB_Prosellodrilus_amplisetosus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Scherotheca_porotheca

[Menu]

```{r  AB_Scherotheca_porotheca , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Scherotheca_porotheca'
titre <- paste('
AB_Scherotheca_porotheca
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Orodrilus_paradoxus_paradoxus

[Menu]

```{r  AB_Orodrilus_paradoxus_paradoxus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Orodrilus_paradoxus_paradoxus'
titre <- paste('
AB_Orodrilus_paradoxus_paradoxus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Octolasion_lacteum_gracile

[Menu]

```{r  AB_Octolasion_lacteum_gracile , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Octolasion_lacteum_gracile'
titre <- paste('
AB_Octolasion_lacteum_gracile
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]

## AB_Flabellodrilus_bartolii

[Menu]

```{r  AB_Flabellodrilus_bartolii , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Flabellodrilus_bartolii'
titre <- paste('
AB_Flabellodrilus_bartolii
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```

[Menu]
