##  AB_Allolobophora_chlorotica_chlorotica
[Menu]
```{r  AB_Allolobophora_chlorotica_chlorotica , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Allolobophora_chlorotica_chlorotica'
titre <- paste('
AB_Allolobophora_chlorotica_chlorotica
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Aporrectodea_caliginosa
[Menu]
```{r  AB_Aporrectodea_caliginosa , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_caliginosa'
titre <- paste('
AB_Aporrectodea_caliginosa
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Aporrectodea_rosea
[Menu]
```{r  AB_Aporrectodea_rosea , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_rosea'
titre <- paste('
AB_Aporrectodea_rosea
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Lumbricus_terrestris
[Menu]
```{r  AB_Lumbricus_terrestris , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_terrestris'
titre <- paste('
AB_Lumbricus_terrestris
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Lumbricus_castaneus
[Menu]
```{r  AB_Lumbricus_castaneus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_castaneus'
titre <- paste('
AB_Lumbricus_castaneus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Aporrectodea_longa_longa
[Menu]
```{r  AB_Aporrectodea_longa_longa , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_longa_longa'
titre <- paste('
AB_Aporrectodea_longa_longa
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Aporrectodea_icterica
[Menu]
```{r  AB_Aporrectodea_icterica , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_icterica'
titre <- paste('
AB_Aporrectodea_icterica
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Aporrectodea_giardi
[Menu]
```{r  AB_Aporrectodea_giardi , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_giardi'
titre <- paste('
AB_Aporrectodea_giardi
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Lumbricus_sp
[Menu]
```{r  AB_Lumbricus_sp , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_sp'
titre <- paste('
AB_Lumbricus_sp
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Aporrectodea_nocturna
[Menu]
```{r  AB_Aporrectodea_nocturna , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_nocturna'
titre <- paste('
AB_Aporrectodea_nocturna
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Satchellius_mammalis
[Menu]
```{r  AB_Satchellius_mammalis , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Satchellius_mammalis'
titre <- paste('
AB_Satchellius_mammalis
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Aporrectodea_sp
[Menu]
```{r  AB_Aporrectodea_sp , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_sp'
titre <- paste('
AB_Aporrectodea_sp
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Aporrectodea_caliginosa_meridionalis
[Menu]
```{r  AB_Aporrectodea_caliginosa_meridionalis , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_caliginosa_meridionalis'
titre <- paste('
AB_Aporrectodea_caliginosa_meridionalis
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Octolasion_cyaneum
[Menu]
```{r  AB_Octolasion_cyaneum , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Octolasion_cyaneum'
titre <- paste('
AB_Octolasion_cyaneum
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Lumbricus_rubellus_rubellus
[Menu]
```{r  AB_Lumbricus_rubellus_rubellus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_rubellus_rubellus'
titre <- paste('
AB_Lumbricus_rubellus_rubellus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Lumbricus_friendi
[Menu]
```{r  AB_Lumbricus_friendi , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_friendi'
titre <- paste('
AB_Lumbricus_friendi
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Murchieona_muldali
[Menu]
```{r  AB_Murchieona_muldali , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Murchieona_muldali'
titre <- paste('
AB_Murchieona_muldali
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Lumbricus_rubellus_castanoides
[Menu]
```{r  AB_Lumbricus_rubellus_castanoides , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_rubellus_castanoides'
titre <- paste('
AB_Lumbricus_rubellus_castanoides
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Lumbricus_centralis
[Menu]
```{r  AB_Lumbricus_centralis , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_centralis'
titre <- paste('
AB_Lumbricus_centralis
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Octolasion_sp
[Menu]
```{r  AB_Octolasion_sp , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Octolasion_sp'
titre <- paste('
AB_Octolasion_sp
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Allolobophora_chlorotica_postepheba
[Menu]
```{r  AB_Allolobophora_chlorotica_postepheba , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Allolobophora_chlorotica_postepheba'
titre <- paste('
AB_Allolobophora_chlorotica_postepheba
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Lumbricus_festivus
[Menu]
```{r  AB_Lumbricus_festivus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_festivus'
titre <- paste('
AB_Lumbricus_festivus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Aporrectodea_indéterminable
[Menu]
```{r  AB_Aporrectodea_indéterminable , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_indéterminable'
titre <- paste('
AB_Aporrectodea_indéterminable
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Proctodrilus_antipai_antipai
[Menu]
```{r  AB_Proctodrilus_antipai_antipai , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Proctodrilus_antipai_antipai'
titre <- paste('
AB_Proctodrilus_antipai_antipai
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Aporrectodea_caliginosa_indéterminable
[Menu]
```{r  AB_Aporrectodea_caliginosa_indéterminable , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_caliginosa_indéterminable'
titre <- paste('
AB_Aporrectodea_caliginosa_indéterminable
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Allolobophora_sp
[Menu]
```{r  AB_Allolobophora_sp , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Allolobophora_sp'
titre <- paste('
AB_Allolobophora_sp
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Lumbricus_castaneus_disjonctus
[Menu]
```{r  AB_Lumbricus_castaneus_disjonctus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_castaneus_disjonctus'
titre <- paste('
AB_Lumbricus_castaneus_disjonctus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Eisenia_fetida
[Menu]
```{r  AB_Eisenia_fetida , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Eisenia_fetida'
titre <- paste('
AB_Eisenia_fetida
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Dendrobaena_octaedra
[Menu]
```{r  AB_Dendrobaena_octaedra , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Dendrobaena_octaedra'
titre <- paste('
AB_Dendrobaena_octaedra
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Aporrectodea_trapezoides
[Menu]
```{r  AB_Aporrectodea_trapezoides , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_trapezoides'
titre <- paste('
AB_Aporrectodea_trapezoides
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Eiseniella_tetraedra
[Menu]
```{r  AB_Eiseniella_tetraedra , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Eiseniella_tetraedra'
titre <- paste('
AB_Eiseniella_tetraedra
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Lumbricus_rubellus_indéterminable
[Menu]
```{r  AB_Lumbricus_rubellus_indéterminable , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_rubellus_indéterminable'
titre <- paste('
AB_Lumbricus_rubellus_indéterminable
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Eisenia_andrei
[Menu]
```{r  AB_Eisenia_andrei , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Eisenia_andrei'
titre <- paste('
AB_Eisenia_andrei
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Aporrectodea_cupulifera
[Menu]
```{r  AB_Aporrectodea_cupulifera , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_cupulifera'
titre <- paste('
AB_Aporrectodea_cupulifera
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Dendrodrilus_rubidus
[Menu]
```{r  AB_Dendrodrilus_rubidus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Dendrodrilus_rubidus'
titre <- paste('
AB_Dendrodrilus_rubidus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Dendrobaena_attemsi
[Menu]
```{r  AB_Dendrobaena_attemsi , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Dendrobaena_attemsi'
titre <- paste('
AB_Dendrobaena_attemsi
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Prosellodrilus_amplisetosus_amplisetosus
[Menu]
```{r  AB_Prosellodrilus_amplisetosus_amplisetosus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Prosellodrilus_amplisetosus_amplisetosus'
titre <- paste('
AB_Prosellodrilus_amplisetosus_amplisetosus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Aporrectodea_georgii
[Menu]
```{r  AB_Aporrectodea_georgii , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_georgii'
titre <- paste('
AB_Aporrectodea_georgii
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Dendrobaena_sp
[Menu]
```{r  AB_Dendrobaena_sp , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Dendrobaena_sp'
titre <- paste('
AB_Dendrobaena_sp
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Avelona_ligra
[Menu]
```{r  AB_Avelona_ligra , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Avelona_ligra'
titre <- paste('
AB_Avelona_ligra
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Octolasion_lacteum_lacteum
[Menu]
```{r  AB_Octolasion_lacteum_lacteum , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Octolasion_lacteum_lacteum'
titre <- paste('
AB_Octolasion_lacteum_lacteum
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Allolobophora_burgondiae
[Menu]
```{r  AB_Allolobophora_burgondiae , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Allolobophora_burgondiae'
titre <- paste('
AB_Allolobophora_burgondiae
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Aporrectodea_ripicola
[Menu]
```{r  AB_Aporrectodea_ripicola , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_ripicola'
titre <- paste('
AB_Aporrectodea_ripicola
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Prosellodrilus_fragilis_indéterminable
[Menu]
```{r  AB_Prosellodrilus_fragilis_indéterminable , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Prosellodrilus_fragilis_indéterminable'
titre <- paste('
AB_Prosellodrilus_fragilis_indéterminable
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Dendrodrilus_rubidus_subrubicundus
[Menu]
```{r  AB_Dendrodrilus_rubidus_subrubicundus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Dendrodrilus_rubidus_subrubicundus'
titre <- paste('
AB_Dendrodrilus_rubidus_subrubicundus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Scherotheca_sp
[Menu]
```{r  AB_Scherotheca_sp , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Scherotheca_sp'
titre <- paste('
AB_Scherotheca_sp
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Microscolex_dubius
[Menu]
```{r  AB_Microscolex_dubius , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Microscolex_dubius'
titre <- paste('
AB_Microscolex_dubius
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Prosellodrilus_sp
[Menu]
```{r  AB_Prosellodrilus_sp , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Prosellodrilus_sp'
titre <- paste('
AB_Prosellodrilus_sp
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Aporrectodea_tuberculata
[Menu]
```{r  AB_Aporrectodea_tuberculata , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_tuberculata'
titre <- paste('
AB_Aporrectodea_tuberculata
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Scherotheca_savignyi_savignyi
[Menu]
```{r  AB_Scherotheca_savignyi_savignyi , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Scherotheca_savignyi_savignyi'
titre <- paste('
AB_Scherotheca_savignyi_savignyi
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Aporrectodea_longa
[Menu]
```{r  AB_Aporrectodea_longa , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_longa'
titre <- paste('
AB_Aporrectodea_longa
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Eisenia_veneta
[Menu]
```{r  AB_Eisenia_veneta , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Eisenia_veneta'
titre <- paste('
AB_Eisenia_veneta
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Aporrectodea_limicola
[Menu]
```{r  AB_Aporrectodea_limicola , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_limicola'
titre <- paste('
AB_Aporrectodea_limicola
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Microscolex_phosphoreus
[Menu]
```{r  AB_Microscolex_phosphoreus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Microscolex_phosphoreus'
titre <- paste('
AB_Microscolex_phosphoreus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Eisenia_sp
[Menu]
```{r  AB_Eisenia_sp , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Eisenia_sp'
titre <- paste('
AB_Eisenia_sp
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Eisenia_fetida_indéterminable
[Menu]
```{r  AB_Eisenia_fetida_indéterminable , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Eisenia_fetida_indéterminable'
titre <- paste('
AB_Eisenia_fetida_indéterminable
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Prosellodrilus_fragilis_fragilis
[Menu]
```{r  AB_Prosellodrilus_fragilis_fragilis , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Prosellodrilus_fragilis_fragilis'
titre <- paste('
AB_Prosellodrilus_fragilis_fragilis
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Lumbricus_friendi_lineatus
[Menu]
```{r  AB_Lumbricus_friendi_lineatus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_friendi_lineatus'
titre <- paste('
AB_Lumbricus_friendi_lineatus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Dendrobaena_cognettii
[Menu]
```{r  AB_Dendrobaena_cognettii , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Dendrobaena_cognettii'
titre <- paste('
AB_Dendrobaena_cognettii
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Dendrobaena_hortensis
[Menu]
```{r  AB_Dendrobaena_hortensis , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Dendrobaena_hortensis'
titre <- paste('
AB_Dendrobaena_hortensis
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Bimastos_eiseni
[Menu]
```{r  AB_Bimastos_eiseni , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Bimastos_eiseni'
titre <- paste('
AB_Bimastos_eiseni
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Allolobophora_chlorotica_indéterminable
[Menu]
```{r  AB_Allolobophora_chlorotica_indéterminable , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Allolobophora_chlorotica_indéterminable'
titre <- paste('
AB_Allolobophora_chlorotica_indéterminable
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Lumbricus_rubellus_friendoides
[Menu]
```{r  AB_Lumbricus_rubellus_friendoides , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_rubellus_friendoides'
titre <- paste('
AB_Lumbricus_rubellus_friendoides
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Haplotaxis_sp
[Menu]
```{r  AB_Haplotaxis_sp , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Haplotaxis_sp'
titre <- paste('
AB_Haplotaxis_sp
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Octodrilus_complanatus
[Menu]
```{r  AB_Octodrilus_complanatus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Octodrilus_complanatus'
titre <- paste('
AB_Octodrilus_complanatus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Lumbricus_meliboeus
[Menu]
```{r  AB_Lumbricus_meliboeus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Lumbricus_meliboeus'
titre <- paste('
AB_Lumbricus_meliboeus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Prosellodrilus_occidentalis_occidentalis
[Menu]
```{r  AB_Prosellodrilus_occidentalis_occidentalis , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Prosellodrilus_occidentalis_occidentalis'
titre <- paste('
AB_Prosellodrilus_occidentalis_occidentalis
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Scherotheca_dinoscolex
[Menu]
```{r  AB_Scherotheca_dinoscolex , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Scherotheca_dinoscolex'
titre <- paste('
AB_Scherotheca_dinoscolex
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Dendrobaena_alpina_zeugochaeta
[Menu]
```{r  AB_Dendrobaena_alpina_zeugochaeta , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Dendrobaena_alpina_zeugochaeta'
titre <- paste('
AB_Dendrobaena_alpina_zeugochaeta
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Microscolex_sp
[Menu]
```{r  AB_Microscolex_sp , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Microscolex_sp'
titre <- paste('
AB_Microscolex_sp
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Hemigastrodrilus_monicae
[Menu]
```{r  AB_Hemigastrodrilus_monicae , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Hemigastrodrilus_monicae'
titre <- paste('
AB_Hemigastrodrilus_monicae
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Prosellodrilus_praticola
[Menu]
```{r  AB_Prosellodrilus_praticola , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Prosellodrilus_praticola'
titre <- paste('
AB_Prosellodrilus_praticola
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Octolasion_lacteum
[Menu]
```{r  AB_Octolasion_lacteum , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Octolasion_lacteum'
titre <- paste('
AB_Octolasion_lacteum
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Scherotheca_savignyi_indéterminable
[Menu]
```{r  AB_Scherotheca_savignyi_indéterminable , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Scherotheca_savignyi_indéterminable'
titre <- paste('
AB_Scherotheca_savignyi_indéterminable
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Aporrectodea_rubra
[Menu]
```{r  AB_Aporrectodea_rubra , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Aporrectodea_rubra'
titre <- paste('
AB_Aporrectodea_rubra
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Scherotheca_rhodana
[Menu]
```{r  AB_Scherotheca_rhodana , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Scherotheca_rhodana'
titre <- paste('
AB_Scherotheca_rhodana
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Pheretima_indéterminable
[Menu]
```{r  AB_Pheretima_indéterminable , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Pheretima_indéterminable'
titre <- paste('
AB_Pheretima_indéterminable
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Prosellodrilus_pyrenaicus
[Menu]
```{r  AB_Prosellodrilus_pyrenaicus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Prosellodrilus_pyrenaicus'
titre <- paste('
AB_Prosellodrilus_pyrenaicus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Scherotheca_nivicola
[Menu]
```{r  AB_Scherotheca_nivicola , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Scherotheca_nivicola'
titre <- paste('
AB_Scherotheca_nivicola
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Panoniona_leoni
[Menu]
```{r  AB_Panoniona_leoni , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Panoniona_leoni'
titre <- paste('
AB_Panoniona_leoni
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Pheritima_Diffringens
[Menu]
```{r  AB_Pheritima_Diffringens , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Pheritima_Diffringens'
titre <- paste('
AB_Pheritima_Diffringens
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Scherotheca_aquitana
[Menu]
```{r  AB_Scherotheca_aquitana , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Scherotheca_aquitana'
titre <- paste('
AB_Scherotheca_aquitana
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Proctodrilus_antipai_indéterminable
[Menu]
```{r  AB_Proctodrilus_antipai_indéterminable , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Proctodrilus_antipai_indéterminable'
titre <- paste('
AB_Proctodrilus_antipai_indéterminable
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Prosellodrilus_amplisetosus
[Menu]
```{r  AB_Prosellodrilus_amplisetosus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Prosellodrilus_amplisetosus'
titre <- paste('
AB_Prosellodrilus_amplisetosus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Scherotheca_porotheca
[Menu]
```{r  AB_Scherotheca_porotheca , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Scherotheca_porotheca'
titre <- paste('
AB_Scherotheca_porotheca
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Orodrilus_paradoxus_paradoxus
[Menu]
```{r  AB_Orodrilus_paradoxus_paradoxus , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Orodrilus_paradoxus_paradoxus'
titre <- paste('
AB_Orodrilus_paradoxus_paradoxus
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Octolasion_lacteum_gracile
[Menu]
```{r  AB_Octolasion_lacteum_gracile , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Octolasion_lacteum_gracile'
titre <- paste('
AB_Octolasion_lacteum_gracile
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



##  AB_Flabellodrilus_bartolii
[Menu]
```{r  AB_Flabellodrilus_bartolii , fig.align='center', fig.height=4, fig.width=4, fig.dpi=150}
var_rep <- 'AB_Flabellodrilus_bartolii'
titre <- paste('
AB_Flabellodrilus_bartolii
& clcm_lvl3')
cat(paste0("- ",titre,"\n"))

box_plot(df = bdd_sp_explo, var_rep = var_rep, predicteur = 'clcm_lvl3', titre_x = 'clcm_lvl3', titre_y = var_rep)
for (i in 1:length(predictors)) {
  cat(paste('- ', var_rep, '&', predictors[i]))
  g <- nuage_point(df = bdd_sp_explo,
                    var_rep = var_rep,
                    predicteur = predictors[i],
                    titre_x = predictors[i],
                    titre_y = var_rep)
  print(g)
}
```
[Menu] 



